---
title: "ReadMe"
author: "BlackPluto"
date: "August 2, 2015"
output: 
  html_document: 
    highlight: tango
    theme: cosmo
---
## The pratice on Kaggle
Titanic: Machine Learning from Disaster[https://www.kaggle.com/c/titanic]    

## Clean the data
Read and prepare the data.
```{r}
suppressMessages(library(ggplot2))
suppressMessages(library(dplyr))
library(doParallel)

train <- read.csv('train.csv')
# check
summary(train)
hist(train$Age)
shapiro.test(train$Age)
qqnorm(train$Age)
median(train$Age, na.rm = T)
train.shaped <- train %>% select(-PassengerId, -Name, -Ticket, -Cabin) %>% 
                mutate(age = ifelse(is.na(Age), 28, Age), 
                       survive = factor(ifelse(Survived == 1, 'Yes', 'No' )), 
                       class = factor(ifelse(Pclass == 1, 'U',
                                             ifelse(Pclass == 2, 'M', 'L')))) %>% 
                select(-Survived, -Pclass, -Age, -Embarked)
summary(train.shaped)

test <- read.csv('test.csv')
test.shaped <- test %>% select(-PassengerId, -Name, -Ticket, -Cabin) %>% 
               mutate(age = ifelse(is.na(Age), 28, Age), 
                      class = factor(ifelse(Pclass == 1, 'U',
                                     ifelse(Pclass == 2, 'M', 'L')))) %>% 
               select(-Pclass, -Age, -Embarked)
```
## the base model, the logistic regression
Use all the variables except the name and cabin. And __here only the complete cases are used.__ And I got about 80% accuracy.

```{r}
base.mod <- glm(data = train.shaped, survive ~ ., family = binomial)
summary(base_mod)
base.prediction <- ifelse(predict(base.mod, type = 'response') > 0.5, 'Yes', 'No')
table(train.shaped$survive, base.prediction)
(base_accuracy <- (467 + 243) / 891) #0.7968575

# decrease the variables
base.mod.min <- glm(data = train.shaped, survive ~ Sex + class + age + SibSp, family = binomial)
base.min.prediction <- ifelse(predict(base.mod.min, type = 'response') > 0.5, 'Yes', 'No')
table(train.shaped$survive, base_min_prediction)
(base_accuracy <- (459 + 243) / 891) #78.78%

# test with the test data set
base.test.result <- ifelse(predict(base.mod.min, newdata = test.shaped) >= 0.5, 1, 0)
#write.csv('base.mod.result.csv', x = data.frame(PassengerId = test$PassengerId, Survived = base.test.result), row.names = F)
```
### The base model result
__Survive ~ Sex + class + age + SibSp__ Got 77.033% right on the test set. Ranked 2249/3146.     

###Now try the caret package
```{r, cache = T}
library(doParallel)
suppressMessages(library(caret))
suppressMessages(library(boot))


cl <- makePSOCKcluster(12)
registerDoParallel(cl)

# not used here
mean_boot <- function(data, id){
    dat <- na.omit(data[id, ]$Age)
    mean(dat)
}
boot(train, mean_boot, 1000)

# do a model selection with k-fold cv, where k = 10
ctrl <- trainControl(method = 'repeatedcv')
mod.lda <- train(data = train.shaped, survive ~ ., method = 'lda2', trControl = ctrl, tuneGrid = data.frame(.dimen=1:6))

mod.knn <- train(data = train.shaped, survive ~ ., method = 'knn', trControl = ctrl, tuneLength = 10)

mod.svm <- train(data = train.shaped, survive ~ ., method = 'svmLinear', trControl = ctrl, preProcess = c('center',             'scale'), tuneGrid = data.frame(.C=seq(0.001, .5, length.out = 12)))

mod.treebag <- train(data = train.shaped, survive ~ ., method = 'treebag', trControl = ctrl)

mod.gbm <- train(data = train.shaped, survive ~ ., method = 'gbm', trControl = ctrl, tuneLength = 10)

mod.randomforest <- train(data = train.shaped, survive ~ ., method = 'rf', trControl = ctrl, tuneLength = 6)

grid <- expand.grid(.trials = 1:30,
                    .model = "tree",
                    .winnow = seq(0, 1, length.out = 15))
mod.c5 <- train(data = train.shaped, survive ~ ., method = "C5.0", tuneGrid = grid)

#do the prediction on the test set
pre.lda <- ifelse(predict(mod.lda, test.shaped) == "Yes", 1, 0)
pre.knn <- ifelse(predict(mod.knn, test.shaped) == "Yes", 1, 0)
pre.svm <- ifelse(predict(mod.svm, test.shaped) == "Yes", 1, 0)
pre.treebag <- ifelse(predict(mod.treebag, test.shaped) == "Yes", 1, 0)
pre.gbm <- ifelse(predict(mod.gbm, test.shaped) == "Yes", 1, 0)
pre.randomforest <- ifelse(predict(mod.randomforest, test.shaped) == "Yes", 1, 0)
pre.c5 <- ifelse(predict(mod.c5, test.shaped) == "Yes", 1, 0)

fare.na.case <- test[is.na(test.shaped$Fare), ]

result <- as.data.frame(cbind(pASSENGERiD = test$PassengerId[!is.na(test$Fare)], pre.lda, pre.knn, pre.svm, pre.treebag, pre.gbm, pre.randomforest, pre.c5))

# predict by human!!
result[418, ] <- c(1044, 0, 0, 0, 0, 0, 0, 0)
#write.csv(result, 'final.result.csv', row.names = F, quote = F) 
stopCluster(cl)
```

And surprisingly, the random forest performes worse than my first logistic model! So now try to use the treebag model.And __NO__!! Still no improvement!
So try to reproduce the base model on the page. "A survival table created based on the proportion of survivors using gender, their ticket class, and the price they paid for their ticket."    

ensamble
================
Two methods:    
-avarage all the 7 models and chose the cutoff avlue at .5. which performed the bset so fat at 0.77512.(Not shown here)
-Build a gbm with 7 additional pros.
```{r}
cl <- makePSOCKcluster(23)
registerDoParallel(cl)
train.shaped$lda <- predict(mod.lda, train.shaped, type = "prob")[, 1] # the prob of NO
train.shaped$knn <- predict(mod.knn, train.shaped, type = "prob")[, 1] # the prob of NO
train.shaped$c5 <- predict(mod.c5, train.shaped, type = "prob")[, 1] # the prob of NO
train.shaped$gbm <- predict(mod.gbm, train.shaped, type = "prob")[, 1] # the prob of NO
train.shaped$svm <- predict(mod.svm, train.shaped) # cannot get the prob.
train.shaped$rf <- predict(mod.randomforest, train.shaped, type = "prob")[, 1] # the prob of NO
train.shaped$bagtree <- predict(mod.treebag, train.shaped, type = "prob")[, 1] # the prob of NO
head(train.shaped)

####
mod.em <- train(data = train.shaped, survive ~ ., method = "xgbTree", trControl = ctrl) # .97... but .55 on test!!!!
mod.em2 <- train(data = train.shaped, survive ~ ., method = "gbm", trControl = ctrl, tuneLength = 10) 
#handle the NA
test.shaped[!complete.cases(test.shaped), "Fare"] <- median(train.shaped$Fare)
test.shaped$lda <- predict(mod.lda, test.shaped, type = "prob")[, 1] # the prob of NO
test.shaped$knn <- predict(mod.knn, test.shaped, type = "prob")[, 1] # the prob of NO
test.shaped$c5 <- predict(mod.c5, test.shaped, type = "prob")[, 1] # the prob of NO
test.shaped$gbm <- predict(mod.gbm, test.shaped, type = "prob")[, 1] # the prob of NO
test.shaped$svm <- predict(mod.svm, test.shaped) # cannot get the prob.
test.shaped$rf <- predict(mod.randomforest, test.shaped, type = "prob")[, 1] # the prob of NO
test.shaped$bagtree <- predict(mod.treebag, test.shaped, type = "prob")[, 1] # the prob of NO
#final output
pre.final <- predict(mod.em, test.shaped)
pre.final2 <- predict(mod.em2, test.shaped)
#write.csv(pre.final2, 'emModel.result2.csv', row.names = F, quote = F) 
stopCluster(cl)
```
